%#! platex UserGuideJa

\section*{Trademarks}
\OFthirdparty{ANSYS} is a registered trademark of ANSYS Inc.\par
\OFthirdparty{CFX} is a registered trademark of AEA Technology Engineering Software Ltd.\par
\OFthirdparty{CHEMKIN} is a registered trademark of Sandia National Laboratories\par
\OFthirdparty{CORBA} is a registered trademark of Object Management Group Inc.\par
\OFthirdparty{openDX} is a registered trademark of International Business Machines Corporation\par
\OFthirdparty{EnSight} is a registered trademark of Computational Engineering International Ltd.\par
\OFthirdparty{AVS}/Express is a registered trademark of Advanced Visual Systems Inc.\par
\OFthirdparty{Fluent} is a registered trademark of Fluent Inc.\par
\OFthirdparty{GAMBIT} is a registered trademark of Fluent Inc.\par
\OFthirdparty{Fieldview} is a registered trademark of Intelligent Light\par
\OFthirdparty{Icem-CFD} is a registered trademark of ICEM Technologies GmbH\par
\OFthirdparty{I-DEAS} is a registered trademark of Structural Dynamics Research Corporation\par
\OFthirdparty{JAVA} is a registered trademark of Sun Microsystems Inc.\par
\OFthirdparty{Linux} is a registered trademark of Linus Torvalds\par
\OFthirdparty{MICO} is a registered trademark of MICO Inc.\par
OpenFOAM is a registered trademark of OpenCFD Ltd.\par
\OFthirdparty{ParaView} is a registered trademark of Kitware\par
\OFthirdparty{STAR-CD} is a registered trademark of Computational Dynamics Ltd.\par
\OFthirdparty{UNIX} is a registered trademark of The Open Group\par
